Six ways to understand monads\\ \small{Experiences from the functional programming course at TU Delft}

### 2012-10-30 latex/paper.tex
Teapot screenshots

\documentclass[conference]{IEEEtran}
\usepackage{graphicx}
\usepackage{times}

@@

@@

\section*{Acknowledgements}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{graphicx}
\usepackage{times}
\usepackage{subfigure}

@@

\begin{figure*}
\centering
\subfigure[Reference, rendered with Java graphics]{
\includegraphics[scale=0.173]{teapot-reference.png}
\label{fig:teapot-reference}
}
\subfigure[Decomposition in Scala, rendered with Java graphics]{
\includegraphics[scale=0.17]{teapot-java-canvas.png}
\label{fig:teapot-scala}
}
\subfigure[Decomposition in Scheme, rendered with appropriately positioned {\sc html} \textsf{div}
elements]{
\includegraphics[scale=0.2]{teapot-html-divs.png}
\label{fig:teapot-html-divs}
}
\subfigure[Decomposition in Javascript, rendered with {\sc html5} graphics]{
\includegraphics[scale=0.31]{teapot-html-canvas.png}
\label{fig:teapot-html-canvas}
}
\label{fig:proj}
\caption[]{Example results from the teapot experiment.}
\end{figure*}

@@

\section*{Acknowledgements and Availability}
